[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-30 reviews/response_reound1.md

> The binary included in the docker image crashes immediately (Illegal
> instruction (core dumped)) on my architecture (described below to ease
> debugging).

Thank you for reporting this issue. We suspect that the Docker container
requires an instruction that your computer does not support. We built the docker
image on the OS Ubuntu 22.04 LTS and the CPU Intel(R) Core(TM) i7-7600U CPU @
2.80GHz.

We could not identify the root cause of the issue. So could you please run the
artifact by cloning the GitHub repository and building a Docker image locally on
your machine? We are happy that at least you successfully built the image on
your machine.

In Section 2 of the revised `README.pdf`, we refer the reader to Section 4.2 if
they have trouble running the prebuilt image.

@@

Thank you for the suggestion.

In Section 4.4 of the revised `README.pdf`, we provide details on how to
recompile (i) the C++ code of the volesti-RaML interface and (i) the OCaml code
of Hybrid RaML. The remaining code, such as the Python scripts, does not need
recompilation after modification.

> Being able to test to analyser on new benchmarks is required to grant the
> "Reusable" badge. It would be helpful to add a small paragraph in the README
> instructing how to do so, and include tools in the docker image to make this
> process easier.

If the user wishes to analyze their custom OCaml program using Hybrid RaML, the
user should first prepare (i) the source file of their OCaml program, augmented
with a collection of inputs for generating runtime cost data and (ii) a
configuration file specifying hyperparameters of Hybrid AARA. To learn the
formats of these files, the user can look at the examples inside the artifact.
Finally, the user runs Hybrid RaML as demonstrated in Section 1 of `README.pdf`.

### 2024-03-31 reviews/response_reound1.md

Thank you for going through the getting-started guide. We are happy that you did
not encounter any technical issues with the artifact.

# Review C

> The binary included in the docker image crashes immediately (Illegal
> instruction (core dumped)) on my architecture (described below to ease
> debugging).

Thank you for reporting this issue. The same error message has been reported in
other Docker images (e.g.,
[here](https://github.com/ultralytics/ultralytics/issues/7085)). We suspect that
the prebuilt Docker image requires an instruction that your computer does not
support. We built the Docker image on the OS Ubuntu 22.04 LTS and the CPU
Intel(R) Core(TM) i7-7600U CPU @ 2.80GHz. We also tested the prebuilt image on
macOS with Apple silicon, and it ran successfully.

We could not identify the root cause of the issue. We believe it is a technical
issue of Docker, rather than our code. As stated on the website of PLDI 2024
Artifact Evaluation, it is recommended to provide prebuilt Docker images (or
VMs), instead of providing scripts for building them. Hence, we will keep the
artifact in the form of a prebuilt Docker image, even though it is not
self-contained anymore if the user has trouble with the prebuilt image.

If you do not mind, could you please run the artifact by cloning the GitHub
repository and building a Docker image locally on your machine? We are happy
that at least you successfully built the image on your machine.

@@

In Section 2 of the revised `README.pdf`, we refer the reader to Section 4.2 if
they have trouble running the prebuilt image.

> It would be good to add instructions in the README to recompile the code
> directly inside the docker, and avoid those crashes. This would additionally
> allow user to tweak the code directly inside the docker, and observe changes
> there.

Thank you for the suggestion.

In Section 4.4 of the revised `README.pdf`, we provide details of how to
recompile (i) the C++ code of the volesti-RaML interface and (i) the OCaml code
of Hybrid RaML. The remaining code, such as the Python scripts, does not need
recompilation after modification.

### 2024-04-05 README/build_and_customize.tex
Minor refactoring
Fixed a typo in README.pdf and added the updated review C

\subsection{Build the Docker Image}

@@

To compile the C++ source code of the volesti-RaML interface, go to the
directory \texttt{/home/hybrid\_aara/volesti\_raml\_interface/bin} and then run
\begin{verbatim}
# cmake .. && cmake --build .
\end{verbatim}

>>>>

\subsection{Build the Docker Image}
\label{sec:Build the Docker Image}

@@

To compile the C++ source code of the volesti-RaML interface, go to the
directory \texttt{/home/hybrid\_aara/volesti\_raml\_interface/build} and then
run
\begin{verbatim}
# cmake .. && cmake --build .
\end{verbatim}
